Tracing the Hercules stream around the Galaxy

### 2010-05-18 tex/hercules.tex
groups-simulations: start on ms
groups-simulations: add distance uncertainties panel
groups-simulations: references in document

\documentclass[12pt,preprint]{aastex}
\usepackage{amssymb,amsmath}
%\usepackage{color,hyperref}
%\definecolor{linkcolor}{rgb}{0,0,0.25}
%\hypersetup{
%  colorlinks=true,        % false: boxed links; true: colored links
%  linkcolor=linkcolor,    % color of internal links
%  citecolor=linkcolor,    % color of links to bibliography
%  filecolor=linkcolor,    % color of file links
%  urlcolor=linkcolor      % color of external links
%}
\setlength{\emergencystretch}{2em}%No overflowing references
\newcommand{\ie}{i.e.}
\newcommand{\etal}{et al.}
\newcommand{\eg}{e.g.}
\newcommand{\eqnname}{equation}
\newcommand{\figurenames}{\figurename s}
\newcommand{\sectionname}{$\mathsection$}
\newcommand{\tvector}[1]{\boldsymbol{\vec{#1}}}
\newcommand{\vx}{\tvector{x}}
\newcommand{\vv}{\tvector{v}}

@@

\title{Probing Galactic structure with moving groups and radial velocity surveys}
\author{Jo~Bovy}%\altaffilmark{1,2}}
\affil{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003, USA}
\email{jb2777@nyu.edu}
%\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics,
%  New York University, 4 Washington Place, New York, NY 10003, USA}
%\altaffiltext{2}{Correspondence should be addressed to jo.bovy@nyu.edu~.}

\begin{abstract}
Various dynamical scenarios related to the Milky Way's bar or spiral
structure have been proposed to explain the existence of moving
groups---clumps of co-moving stars---in the Solar neighborhood. Since
the observed pattern of moving groups is very sensitive to the
properties of the non-axisymmetric feature that creates them, these
moving groups can be a powerful tool in constraining the dynamical
structure of the inner Milky Way. However, at present the various
models are hard to confirm and distinguish with observations of the
local Galactic neighborhood. We show that future programs that survey
the Milky Way disk's kinematics on a more global scale can distinguish
between these models. By integrating orbits of stars in various
steady-state and transient bar and spiral structure potentials that
produce the pattern of moving groups observed in the Solar
neighborhood, we predict the velocity distribution as a function of
location in the Galactic disk. We identify the locations that
distinguish most clearly between the various scenarios. Future
infrared radial velocity surveys can probe the velocity distribution
at these locations. We predict the distribution of radial velocities
that can be directly compared to observations to establish the origin
of the moving groups and to constrain the structural and dynamical
parameters of the non-axisymmetric Milky Way potential.
\end{abstract}

@@

@@

We follow Dehnen's approach \citep{dehnen00a}.

\subsection{Bar potential}

\subsection{Steady-state spiral structure potential}

\subsection{Transient spiral structure potential}

@@

\bibitem[{{Binney} \& {Tremaine}(2008)}]{binneytremaine}
{Binney},~J. \& {Tremaine},~S., 2008, {Galactic Dynamics: Second Edition}
  (Princeton University Press)

@@

@@

@@

>>>>

\documentclass[12pt,preprint]{aastex}
\usepackage{amssymb,amsmath}
%\usepackage{color,hyperref}
%\definecolor{linkcolor}{rgb}{0,0,0.25}
%\hypersetup{
%  colorlinks=true,        % false: boxed links; true: colored links
%  linkcolor=linkcolor,    % color of internal links
%  citecolor=linkcolor,    % color of links to bibliography
%  filecolor=linkcolor,    % color of file links
%  urlcolor=linkcolor      % color of external links
%}
\setlength{\emergencystretch}{2em}%No overflowing references
\newcommand{\ie}{i.e.}
\newcommand{\etal}{et al.}
\newcommand{\eg}{e.g.}
\newcommand{\eqnname}{equation}
\newcommand{\figurenames}{\figurename s}
\newcommand{\sectionname}{$\mathsection$}
\newcommand{\tvector}[1]{\boldsymbol{\vec{#1}}}
\newcommand{\vx}{\tvector{x}}
\newcommand{\vv}{\tvector{v}}
\newcommand{\Gaia}{\emph{Gaia}}

@@

\title{Tracing the Hercules stream around the Galaxy}
\author{Jo~Bovy}%\altaffilmark{1,2}}
\affil{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003, USA}
\email{jb2777@nyu.edu}
%\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics,
%  New York University, 4 Washington Place, New York, NY 10003, USA}
%\altaffiltext{2}{Correspondence should be addressed to jo.bovy@nyu.edu~.}

\begin{abstract}
%Various dynamical scenarios related to the Milky Way's bar or spiral
%structure have been proposed to explain the existence of moving
%groups---clumps of co-moving stars---in the Solar neighborhood. Since
%the observed pattern of moving groups is very sensitive to the
%properties of the non-axisymmetric feature that creates them, these
%moving groups can be a powerful tool in constraining the dynamical
%structure of the inner Milky Way. However, at present the various
%models are hard to confirm and distinguish with observations of the
%local Galactic neighborhood. We show that future programs that survey
%the Milky Way disk's kinematics on a more global scale can distinguish
%between these models. By integrating orbits of stars in various
%steady-state and transient bar and spiral structure potentials that
%produce the pattern of moving groups observed in the Solar
%neighborhood, we predict the velocity distribution as a function of
%location in the Galactic disk. We identify the locations that
%distinguish most clearly between the various scenarios. Future
%infrared radial velocity surveys can probe the velocity distribution
%at these locations. We predict the distribution of radial velocities
%that can be directly compared to observations to establish the origin
%of the moving groups and to constrain the structural and dynamical
%parameters of the non-axisymmetric Milky Way potential.
\end{abstract}

@@

baryon acoustic feature, coincidence problem

@@

We follow Dehnen's approach \citep{dehnen00a}. Only planar.

\section{Two-dimensional velocity distributions}

\section{The line-of-sight velocity distribution}

\section{Discussion}

\subsection{\Gaia}

\subsection{Radial velocity surveys}

SDSS-III Project Description\footnote{Available at
  \url{http://sdss3.org/collaboration/description.pdf}~.}

@@

%\bibitem[{{Binney} \& {Tremaine}(2008)}]{binneytremaine}
%{Binney},~J. \& {Tremaine},~S., 2008, {Galactic Dynamics: Second Edition}
%  (Princeton University Press)

\bibitem[Bailer-Jones(2008)]{bailerjones08a}
  Bailer-Jones, ~C.~A.~L., 2008,
  in IAU Symp.~254, ed.~J.~Andersen, J.~Bland-Hawthorn, and B.~Nordstr\"{o}m, (Dordrecht: Kluwer), 475

\bibitem[Bensby \etal(2007)]{Bensby07a}
  Bensby,~T., \etal, 2007,
  \apjl, 655, L89

\bibitem[Blaauw(1970)]{Blaauw70a}
  Blaauw,~A., 1970, in IAU Symp.~38, ed.~W.~Becker \& I.~Kontopoulos (Dordrecht: Reidel), 199

\bibitem[Blitz \& Spergel(1991)]{blitz91a}
  Blitz,~L.~\& Spergel,~D.~N., 1991, \apj, 379, 631

\bibitem[Binney, Gerhard, \& Spergel(1997)]{binney97a}
  Binney,~J.~J., Gerhard,~O., \& Spergel,~D.~N., 1997,
  \mnras, 288, 365

\bibitem[Bissantz \& Gerhard(2002)]{bissantz02a}
  Bissantz,~N.~\& Gerhard,~O., 2002,
  \mnras, 330, 591

@@

\bibitem[Bovy \& Hogg(2010)]{Bovy10a} Bovy,~J.~\& Hogg,~D.~W., 2010,
  \apj, in press

\bibitem[Caloi \etal(1999)]{caloi99a}
  Caloi,~V.~, \etal, 1999,
  \aap, 351, 925

\bibitem[Cole \& Weinberg(2002)]{cole02a}
  Cole,~A.~A.~\& Weinberg,~M.~D., 2002,
  \apjl, 574, L43

\bibitem[{{Dehnen}(1998)}]{Dehnen98b}
Dehnen,~W., 1998, \aj, 115, 2384

\bibitem[Dehnen(1999a)]{dehnen99a}
  Dehnen,~W., 1999a, \aj, 118, 1190

\bibitem[Dehnen(1999b)]{dehnen99b}
  Dehnen,~W., 1999b, \aj, 118, 1201

\bibitem[Dehnen(1999c)]{dehnen99c}
  Dehnen,~W., 1999c, \apj, 524, L35

@@

\bibitem[Fux(2001)]{fux01a}
  Fux,~R., 2001,
  \aap, 373, 511

\bibitem[Gardner \& Flynn(2010)]{gardner10a}
  Gardner,~E.~\& Flynn,~C., 2010,
  \mnras, in press

\bibitem[H\"{a}fner \etal(2000)]{hafner00}
  H\"{a}fner,~R., \etal, 2000,
  \mnras, 314, 433

\bibitem[Minchev \& Famaey(2009)]{minchev09a}
  Minchev,~I.~\& Famaey,~B., 2009,
  \apj L, submitted

\bibitem[Raboud \etal(1998)]{raboud98a}
  Raboud,~D., \etal, 1998,
  \aap, 335, L61

\bibitem[Shen \etal(2010)]{Shen10a}
  Shen,~J., \etal, 2010, \apj L, submitted

\bibitem[Sellwood \& Binney(2002)]{sellwood02a}
  Sellwood,~J.~A.~\& Binney,~J.J., 2002,
  \mnras, 336, 785

\bibitem[Shu(1969)]{shu69a}
  Shu,~F.~H., 1969,
  \apj, 158, 505

\bibitem[Skuljan, Hearnshaw, \& Cottrell(1999)]{Skuljan99a}
  Skuljan,~J., Hearnshaw,~J.~B., \& Cottrell,~P.~L., 1999, \mnras, 308, 731

@@

\clearpage
\begin{figure}
\includegraphics[width=0.5\textwidth]{veldist.eps}
\caption{observed}\label{fig:obs}
\end{figure}

\clearpage
\begin{figure}
\includegraphics[width=\textwidth]{rphi2d.ps}
\caption{2D}\label{fig:rphi2d}
\end{figure}

\clearpage
\begin{figure}
\includegraphics[width=\textwidth]{rphi1d.ps}\\
\includegraphics[width=\textwidth]{rphi1d2.ps}
\caption{1D}\label{fig:rphi1d}
\end{figure}

\clearpage
\begin{figure}
\includegraphics[width=0.5\textwidth]{detecta.ps}
\includegraphics[width=0.5\textwidth]{detectb.ps}
\caption{detect}\label{fig:detect}
\end{figure}

\clearpage
\begin{figure}
\includegraphics[width=0.5\textwidth]{distuncertain.ps}
\includegraphics[width=0.5\textwidth]{df.ps}\\
\includegraphics[width=0.5\textwidth]{slope.ps}
\includegraphics[width=0.5\textwidth]{barstrength.ps}
\caption{1dvar}\label{fig:1dvar}
\end{figure}
